Test susieI using whole genome, s40.22 samples

### 2020-11-14 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
more PIP cali

@@

}

```

@@

```{r pip1susie, fig.height=4, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP (low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)" )
gridExtra::grid.arrange(f1, f2, ncol =2)
```

@@

@@

@@

```{r pip1ser, fig.height=4, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="SER", main = "PIP (low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="SER", main = "PIP(high power)" )
gridExtra::grid.arrange(f1, f2, ncol =2)
```

```{r scatter1ser, fig.height=4, fig.width=10}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

@@

```{r pip6ser, fig.height=4, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="SER", main = "PIP (low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="SER", main = "PIP(high power)" )
gridExtra::grid.arrange(f1, f2, ncol =2)
```

```{r scatter6ser, fig.height=4, fig.width=10}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

@@

```{r pip7ser, fig.height=4, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="SER", main = "PIP (low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="SER", main = "PIP(high power)" )
gridExtra::grid.arrange(f1, f2, ncol =2)
```

```{r scatter7ser, fig.height=4, fig.width=10}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

>>>>

.obn <- function(pips, ifcausal, mode = c("PIP", "FDR")){
  a_bin <- cut(pips, breaks= seq(0, 1, by=0.1))
  if (mode == "PIP") {
    ob = c(by(ifcausal, a_bin, FUN = sum))
  } else if (mode == "FDR"){
    ob = c(by((1-ifcausal), a_bin, FUN = sum))
  }
  return(ob)
}

nca_plot <- function(pips, ifcausal, runtag = NULL, mode = c("PIP", "FDR"), main = mode[1], ...){

  # ifcausal:0,1, runtag: for adding std.
  if (is.null(runtag)){
     se = 0 
  } else{
    dflist <- list()
    for (rt in unique(runtag)){
      pips.rt <- pips[runtag == rt]
      ifcausal.rt <- ifcausal[runtag == rt]
      dflist[[rt]] <- .obn(pips.rt, ifcausal.rt, mode = mode)
    }
    nca_mean <- colMeans(do.call(rbind, dflist))
    se <- apply(do.call(rbind, dflist), 2, plotrix::std.error)
  }

  df <- data.frame("ncausal" = nca_mean, "se" = se )

  fig <- ggplot(df) +
    geom_bar( aes(x=seq(0, 1, by=0.1)[1:10]+0.05, y=ncausal), color ="black", stat="identity", fill="salmon", alpha=0.7, width = 0.1) +
    geom_errorbar( aes(x= seq(0, 1, by=0.1)[1:10] + 0.05, ymin= ncausal-se, ymax=ncausal+se), width=0.05, colour="black", alpha=0.9, size=0.5) +
    ggtitle(main) +
    xlab("PIP") + ylab("No. causal genes")
    theme_cowplot()
  return(fig)
}

ncausal_plot <- function(pipfs, format = "susie", main = "PIP"){
  df <- NULL
  for (i in 1:length(pipfs)) {
    res <- fread(pipfs[i], header = T)
    res <- data.frame(res[res$type  =="gene", ])
    res$runtag <- i
    if (format == "susie"){
       res <- rename(res, c("susie_pip" = "pip"))
    } else if (format == "SER"){
       res <- rename(res, c("SERpip" = "pip"))
    }
    res <- res[complete.cases(res),]
    df <- rbind(df, res)
  }

  fig <- nca_plot(df$pip, df$ifcausal, df$runtag, mode ="PIP", main = main)
  return(fig)
}

@@

}
```

@@

```{r pip1susie, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)" )
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

@@

```{r pip6susie, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)" )
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter6susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r pip8susie, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)" )
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter8susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

@@

```{r pip1ser, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="SER", main = "PIP(low power)")
f2 <- caliPIP_plot(susieIfs2[6:10], format ="SER", main = "PIP(high power)")
f3 <- ncausal_plot(susieIfs2[1:5], format = "SER", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "SER", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter1ser, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

@@

```{r pip6ser, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="SER", main = "PIP(low power)")
f2 <- caliPIP_plot(susieIfs2[6:10], format ="SER", main = "PIP(high power)")
f3 <- ncausal_plot(susieIfs2[1:5], format = "SER", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "SER", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter6ser, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```

@@

```{r pip7ser, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="SER", main = "PIP(low power)")
f2 <- caliPIP_plot(susieIfs2[6:10], format ="SER", main = "PIP(high power)")
f3 <- ncausal_plot(susieIfs2[1:5], format = "SER", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "SER", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter7ser, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "SER", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "SER", main = "high power")
```
